### 2021-07-21 paper/paper.tex
additional TODO notes

@@

TODO %TODO
\begin{itemize}
  \item Basic design of Trixi.jl and its capabilities
  \item PID comparison of Fluxo and Trixi.jl
  \item Discussion on Julia for numerical simulation science
  \item Prepare repro repo including scripts for Trixi.jl and Fluxo
  \item Cite \cite{bezanson2017julia,schlottkelakemper2021purely,rackauckas2017differentialequations,revels2016forward}
  \item Change title to something like ``Adaptive high-order numerical simulations
  of hyperbolic PDEs with Trixi.jl. A case study of Julia for scientific computing''?
\end{itemize}

\section{Design of Trixi.jl and feature overview}

@@

@@

%\vadjust{\vfill\pagebreak}

@@

\subsection{Handling references}
\label{subsub:references}
References are most easily (and correctly) generated using the
BIBTEX, which is easily invoked via
\begin{verbatim}
\bibliographystyle{juliacon}
\bibliography{ref}
\end{verbatim}
When submitting the document source (.tex) file to external
parties, the ref.bib file should be sent with it.
Don't forget to cite \cite{bezanson2017julia}.

>>>>

\section*{TODO}

\begin{itemize}
  \item Basic design of Trixi.jl and its capabilities
  \item PID comparison of Fluxo and Trixi.jl
  \item Discussion on Julia for numerical simulation science
  \item Prepare repro repo including scripts for Trixi.jl and Fluxo
  \item Cite \cite{bezanson2017julia,schlottkelakemper2021purely,rackauckas2017differentialequations,revels2016forward,ranocha2021sbp}
  \item Change title to something like ``Adaptive high-order numerical simulations
  of hyperbolic PDEs with Trixi.jl: A case study of Julia for scientific computing''?
  \item Restructure non-conservative stuff and add MHD benchmarks?
\end{itemize}

@@

\section{Design of Trixi.jl and overview of its features}

@@

TODO: Add your funding sources (if any) %TODO

@@

% \vadjust{\vfill\pagebreak}

@@
